---
title: "Judges Report"
author: "Philip Chase"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(readxl)
library(janitor)
library(httr)
library(kableExtra)
```

```{r event_facts}
matches <- tribble(
  ~event_code, ~date, ~name, ~divisions, ~notebook_file, ~interview_file,
  "RE-VIQC-22-8238", "10-Dec-2022", "WWR December Blended (MS/ES) VEX IQ Tournament", 2,
  "/Users/pbchase/git/vex_matches/output/P & C Robotic Notebooks for 12-10-2022.csv", "",
  "RE-VIQC-21-4702", "6-Nov-2021", "WWR November Pitching In Tournament", 2, "", ""
) %>%
  mutate(notebook_file = if_else(
    !is.na(notebook_file) & notebook_file != "",
    notebook_file,
    here::here("output", paste(event_code, "notebooks.csv", sep = "_"))
  )) %>%
  mutate(interview_file = if_else(
    !is.na(interview_file) & interview_file != "",
    interview_file,
    here::here("output", paste(event_code, "interviews.csv", sep = "_"))
  )) %>%
  mutate(scratch_file = 
    here::here("output", paste(event_code, "scratches.csv", sep = "_")
  )) %>%
  mutate(event_number_for_url = paste0("4", str_remove(event_code, ".*-"))) %>%
  mutate(team_list_url = paste("https://www.robotevents.com/eventEntities",
    event_number_for_url,
    "teamsReport",
    sep = "/"
  )) %>%
  mutate(skills_url = paste("https://www.robotevents.com/eventEntities",
    event_number_for_url,
    "skillsReport",
    sep = "/"
  )) %>%
  mutate(results_url = paste("https://www.robotevents.com/eventEntities",
    event_number_for_url,
    "resultsReport/",
    sep = "/"
  ))

match <- matches %>%
  filter(event_code == "RE-VIQC-22-8238")

# match <- matches %>%
#   filter(event_code == "RE-VIQC-21-4702")

get_xls_from_url <- function(my_url, use_cached_data = TRUE) {
  if (!fs::dir_exists("cache")) {
    fs::dir_create("cache")
  }
  cached_file_name <- here::here("cache", paste0(fs::path_sanitize(my_url), ".xls"))
  if (!fs::file_exists(cached_file_name) | !use_cached_data) {
    message("Fetching data from ", my_url)
    httr::GET(url = my_url, write_disk(cached_file_name, overwrite = T))  
  } else {
    message("Using cached data for ", my_url)
  }
  df <- readxl::read_xls(cached_file_name) %>%
    janitor::clean_names()
  return(df)
}

teams <- get_xls_from_url(match$team_list_url)
```

```{r make_empty_files}
if (!fs::dir_exists("output")) {
  fs::dir_create("output")
}

# Write out an empty Interviews file if it is does not exist
if (!fs::file_exists(match$interview_file)) {
  checked_in_teams %>%
  select(team) %>%
  mutate(interview_score = NA) %>%
    write_csv(match$interview_file, na = "")
}

# Write out an empty notebooks file if it is does not exist
if (!fs::file_exists(match$notebook_file)) {
  checked_in_teams %>%
  select(team) %>%
  mutate(notebook_score = NA) %>%
  write_csv(match$notebook_file, na = "")
}

# Write out an scratch file if it is does not exist
if (!fs::file_exists(match$scratch_file)) {
  teams %>%
  select(team) %>%
  mutate(scratch = 0) %>%
  write_csv(match$scratch_file, na = "")
}
```

```{r arrival_data, echo=FALSE, include=FALSE}
# read the list of scratches from the Event Partner
scratches <- read_csv(match$scratch_file) %>%
  janitor::clean_names() %>%
  filter(scratch == 1) %>%
  mutate(team = toupper(team)) %>%
  pull(team)

checked_in_teams <- teams %>%
  filter(! team %in% scratches)

registered_team_count = nrow(teams)
scratched_team_count = length(scratches)
checked_in_team_count = nrow(checked_in_teams)

```

## Counts

- Registered team count: `r registered_team_count`
- Scratched team count: `r scratched_team_count`

## List of scratched teams
`r scratches`

```{r judging_data, warning=FALSE, echo=FALSE, include=FALSE}
notebooks <- read_csv(match$notebook_file) %>%
  janitor::clean_names() %>%
  mutate(team = toupper(team)) %>%
  filter(!is.na(team)) %>%
  arrange(desc(notebook_score)) %>%
  mutate(notebook_rank = if_else(
    is.na(notebook_score) | notebook_score == 0,
    NA_integer_,
    row_number()
  ))

# Judged teams not in registrants
notebook_data_not_in_registrants <- notebooks %>%
  anti_join(checked_in_teams, by="team") %>%
  select(team, notebook_score, notebook_rank)

# registrants not in judged teams
registrants_not_in_notebook_data <- checked_in_teams %>%
  anti_join(notebooks, by="team")

interviews <- read_csv(match$interview_file) %>%
  arrange(desc(interview_score)) %>%
  mutate(interview_rank = if_else(
    is.na(interview_score) | interview_score == 0,
    NA_integer_,
    row_number()
  ))

interviews_completed <- interviews %>%
  filter(!is.na(interview_score)) %>%
  nrow()

interviews_remaining <- nrow(checked_in_teams) - interviews_completed

teams_without_an_interview_score <- interviews %>%
  filter(!team %in% scratches) %>%
  filter(is.na(interview_score)) %>%
  select(team)

some_interviews_remain = interviews_remaining > 0

judging <- checked_in_teams %>%
  select(team) %>%
  left_join(notebooks, by = "team") %>%
  left_join(interviews, by = "team") %>%
  mutate(judged_score = notebook_score + interview_score) %>%
  arrange(desc(judged_score)) %>%
  mutate(judged_rank = if_else(is.na(judged_score), NA_integer_, row_number()))
```

## Notebook data not in registrants

`r kbl(notebook_data_not_in_registrants) %>%
  kable_styling()`

## Registrants not in notebook data

`r kbl(registrants_not_in_notebook_data) %>%
  kable_styling()`

## Interviews

- Interviewed team count: `r interviews_completed`
- Interviews remaining: `r interviews_remaining`

```{r interviews_remaining, eval=some_interviews_remain}
print("These teams still need to be recorded in the interview file:")

kbl(teams_without_an_interview_score) %>%
  kable_styling()
```

```{r skills, warning=FALSE, include = FALSE, message = TRUE}
# get results of skills competition
skills_results <- get_xls_from_url(match$skills_url)
if (nrow(skills_results) > 0) {
  skills_data <- skills_results %>%
    janitor::clean_names() %>%
    pivot_wider(
      id_cols = c("rank", "team"),
      names_from = c("type"),
      values_from = c("highscore", "attempts")
    ) %>%
    rowwise() %>%
    mutate(highscore_combined = sum(highscore_driver, highscore_programming, na.rm = TRUE)) %>%
    ungroup() %>%
    select(rank, team, highscore_combined, everything()) %>%
    rename(skills_rank = rank)
} else {
  skills_data <- tribble(
    ~skills_rank, ~team, ~highscore_combined, ~highscore_driver, ~highscore_programming,
    1, "asdf", 1, 1, 1
  ) %>% filter(F)
}
```

```{r qualifier_function}
get_qualifier_results_for_division <- function(base_results_url, division) {
  results_url <- paste0(base_results_url, division)
  results <- get_xls_from_url(results_url)
  data <-
    results %>%
    janitor::clean_names() %>%
    rename_with(., ~ gsub("_[0-9]+", "", .x), contains("_team_")) %>%
    pivot_longer(
      cols = c(red_team, blue_team),
      names_to = c("team_color"),
      values_to = c("team_number")
    ) %>%
    pivot_longer(
      cols = c(red_score, blue_score),
      values_to = c("team_score")
    ) %>%
    mutate(team_color = gsub("_team", "", team_color)) %>%
    mutate(name = gsub("_score", "", name)) %>%
    filter(team_color == name) %>%
    mutate(division = division) %>%
    select(division, match, team_color, team_number, team_score)

  return(data)
}
```

```{r qualifiers}
qualifier_results <- tribble(
  ~division, ~match, ~team_color, ~team_number, ~team_score,
  1, "a", "b", "c", 99
) %>% filter(F)

for (division in seq.int(1, match$divisions)) {
  qualifier_results <- bind_rows(qualifier_results, get_qualifier_results_for_division(match$results_url, division = division))
  }

ranked_qualifer_results <- qualifier_results %>%
  rename(team = team_number) %>%
  group_by(team) %>%
  summarize(average_score = mean(team_score, na.rm = T)) %>%
  arrange(desc(average_score)) %>%
  mutate(qualifier_rank = if_else(!is.na(average_score),
    row_number(),
    NA_integer_
  ))
```

```{r excellence_scores}
excellence_skills_count <- max(nrow(skills_data) * 0.2, 5)
excellence_qualifiers_count <- max(nrow(ranked_qualifer_results) * 0.3, 10)
excellence_criteria = c(
  "has_a_notebook",
  "has_an_interview",
  "top_of_skills",
  "top_of_qualifiers"
)
excellence_scores <-
  judging %>%
  # must have a notebook
  mutate(has_a_notebook = !is.na(notebook_score) & notebook_score != 0) %>%
  # must have an interview
  mutate(has_an_interview = !is.na(interview_score) & interview_score != 0) %>%
  # must be in the top 5 or 20% of skills scores
  left_join(
    skills_data %>%
      arrange(skills_rank) %>%
      mutate(top_of_skills = (row_number() <= excellence_skills_count)),
    by = "team"
  ) %>%
  left_join(
    ranked_qualifer_results %>%
      mutate(top_of_qualifiers = (row_number() <= excellence_qualifiers_count)),
    by = "team"
  ) %>%
  rowwise() %>%
  mutate(combined_rank = sum(judged_rank, skills_rank, qualifier_rank)) %>%
  mutate(combined_excellence_criteria = sum(has_a_notebook, has_an_interview, top_of_skills, top_of_qualifiers)) %>%
  arrange(
    desc(combined_excellence_criteria),
    combined_rank,
    judged_rank,
    notebook_rank,
    interview_rank,
    skills_rank,
    qualifier_rank,
    highscore_driver,
    highscore_programming
  ) %>%
  ungroup() %>%
  mutate(excellence_rank = row_number()) %>%
  select(
    team,
    any_of(excellence_criteria),
    combined_excellence_criteria,
    combined_rank,
    judged_rank,
    notebook_rank,
    interview_rank,
    skills_rank,
    qualifier_rank,
    highscore_combined,
    highscore_driver,
    highscore_programming
  ) %>%
  # Display to top of the rankings
  filter(combined_excellence_criteria >= 3 | row_number() <= 10)
```
## Excellence ranking

The first four criteria are the Excellence award criteria that can be assessed directly from the data. `combined_excellence_criteria` is the sum of those four criteria. `combined_rank` is the sum of the judging rank, skills rank and qualifiers rank. 

`r kbl(excellence_scores) %>%
  kable_styling()`


```{r design_scores}
design_criteria = c(
  "has_a_notebook",
  "has_an_interview"
)
design_scores <-
  judging %>%
  # must have a notebook
  mutate(has_a_notebook = !is.na(notebook_score) & notebook_score != 0) %>%
  # must have an interview
  mutate(has_an_interview = !is.na(interview_score) & interview_score != 0) %>%
  rowwise() %>%
  mutate(combined_design_criteria = sum(has_a_notebook, has_an_interview)) %>%
  filter(combined_design_criteria == 2) %>%
  arrange(
    notebook_rank,
    judged_rank,
    interview_rank
  ) %>%
  ungroup() %>%
  select(
    team,
    any_of(design_criteria),
    notebook_rank,
    judged_rank,
    interview_rank
  )
```
## Design ranking

Only the top 10 teams that have both a notebook score and an interview score are shown.  The teams are sorted by Notebook rank and then total judged rank.

`r kbl(design_scores %>% filter(row_number() <= 10)) %>%
  kable_styling()`


```{r judges_scores}
judges_criteria = c(
  "has_an_interview"
)
judges_scores <-
  judging %>%
  # must have an interview
  mutate(has_an_interview = !is.na(interview_score) & interview_score != 0) %>%
  rowwise() %>%
  mutate(combined_judges_criteria = sum(has_an_interview)) %>%
  filter(combined_judges_criteria == 1) %>%
  arrange(
    interview_rank,
    judged_rank,
    notebook_rank
  ) %>%
  ungroup() %>%
  select(
    team,
    any_of(judges_criteria),
    interview_rank,
    judged_rank,
    notebook_rank
  ) %>%
  # Display to top of the rankings
  filter(row_number() <= 20)
```
## Judges award ranking

Only the top 20 teams that have an interview score are shown. The teams are sorted by interview rank and then total judged rank.

`r kbl(judges_scores) %>%
  kable_styling()`

## Innovate award ranking

The Innovate Award uses the same hard criteria as the Design Award. The top 10 teams that meet those hard criteria are again shown here.

`r kbl(design_scores %>% filter(row_number() <= 10)) %>%
  kable_styling()`


```{r think_scores}
think_skills_count <- max(nrow(skills_data) * 0.2, 5)
think_criteria = c(
  "has_an_interview",
  "has_a_notebook",
  "has_a_skills_score",
  "has_a_programming_skills_score"
)
think_scores <-
  judging %>%
  # must have a notebook
  mutate(has_a_notebook = !is.na(notebook_score) & notebook_score != 0) %>%
  # must have an interview
  mutate(has_an_interview = !is.na(interview_score) & interview_score != 0) %>%
  # must have a programming score
  left_join(
    skills_data %>%
      # must have a skills score
      mutate(has_a_skills_score = !is.na(skills_rank)) %>%
      # must have a programming score
      arrange(desc(highscore_programming)) %>%
      mutate(programming_skills_rank = if_else(is.na(highscore_programming), as.integer(NA) , row_number())) %>%
      mutate(has_a_programming_skills_score = !is.na(programming_skills_rank)),
    by = "team"
  ) %>%
  rowwise() %>%
  mutate(combined_rank = sum(interview_rank, programming_skills_rank)) %>%
  mutate(combined_think_criteria = sum(has_a_notebook, has_an_interview, has_a_skills_score, has_a_programming_skills_score)) %>%
  arrange(
    desc(combined_think_criteria),
    combined_rank,
    interview_rank,
    programming_skills_rank,
    notebook_rank
  ) %>%
  ungroup() %>%
  mutate(think_rank = row_number()) %>%
  select(
    team,
    any_of(think_criteria),
    combined_think_criteria,
    combined_rank,
    interview_rank,
    programming_skills_rank,
    notebook_rank
  ) %>%
  # Display to top of the rankings
  filter(combined_think_criteria >= 3 & row_number() <= 15)
```
## Think ranking

The first four criteria are the Think award criteria that can be assessed directly from the data. The notebook requirement is not a clearly stated criteria, but given the number of judged criteria relating to programming it could be hard to assess those criteria without a notebook so it is included. `combined_think_criteria` is the sum of those four criteria. `combined_rank` is the sum of the interview rank and skills programming rank. 

`r kbl(think_scores) %>%
  kable_styling()`



```{r amaze_scores}
amaze_skills_count <- max(nrow(skills_data) * 0.2, 5)
amaze_criteria = c(
  "has_an_interview",
  "has_a_programming_skills_score",
  "has_a_driver_skills_score",
  "has_a_qualifier_rank"
)
amaze_scores <-
  judging %>%
  # must have an interview
  mutate(has_an_interview = !is.na(interview_score) & interview_score != 0) %>%
  # must have a programming score
  left_join(
    skills_data %>%
      # must have a programming score
      arrange(desc(highscore_programming)) %>%
      mutate(programming_skills_rank = if_else(is.na(highscore_programming), as.integer(NA), row_number())) %>%
      mutate(has_a_programming_skills_score = !is.na(programming_skills_rank)),
    by = "team"
  ) %>%
  # Add driver skills rank
  left_join(
    skills_data %>%
      arrange(desc(highscore_driver)) %>%
      mutate(driver_skills_rank = if_else(is.na(highscore_driver), as.integer(NA), row_number())) %>%
      mutate(has_a_driver_skills_score = !is.na(driver_skills_rank)) %>%
      select(team, has_a_driver_skills_score, driver_skills_rank),
    by = "team"
  ) %>%
  left_join(
    ranked_qualifer_results %>%
      mutate(has_a_qualifier_rank = is.na(qualifier_rank)),
    by = "team"
  ) %>%
  rowwise() %>%
  mutate(combined_rank = sum(interview_rank, programming_skills_rank, driver_skills_rank, qualifier_rank)) %>%
  mutate(combined_amaze_criteria = sum(
    has_an_interview,
    has_a_programming_skills_score,
    has_a_driver_skills_score,
    has_a_qualifier_rank
    )) %>%
  arrange(
    desc(combined_amaze_criteria),
    combined_rank,
    interview_rank,
    programming_skills_rank,
    driver_skills_rank,
    qualifier_rank
  ) %>%
  ungroup() %>%
  mutate(amaze_rank = row_number()) %>%
  select(
    team,
    any_of(amaze_criteria),
    combined_amaze_criteria,
    combined_rank,
    interview_rank,
    programming_skills_rank,
    driver_skills_rank,
    qualifier_rank
  ) %>%
  # Display to top of the rankings
  filter(combined_amaze_criteria >= 3 & row_number() <= 15)
```
## Amaze ranking

The first five criteria are the Amaze award criteria that can be assessed directly from the data.  `combined_amaze_criteria` is the sum of those five criteria. `combined_rank` is the sum of the interview rank, programming skills rank, driver skills rank, and qualifier rank. 

`r kbl(amaze_scores) %>%
  kable_styling()`


```{r build_scores}
build_criteria = c(
  "has_an_interview"
)
build_scores <- judging %>%
  # must have an interview
  mutate(has_an_interview = !is.na(interview_score) & interview_score != 0) %>%
  rowwise() %>%
  mutate(combined_build_criteria = sum(
    has_an_interview
    )) %>%
  arrange(
    desc(combined_build_criteria),
    interview_rank
  ) %>%
  ungroup() %>%
  mutate(interview_rank = row_number()) %>%
  # correct rank when scores are equal
  group_by(interview_score) %>%
  mutate(interview_rank = min(interview_rank)) %>%
  ungroup() %>%
  select(
    team,
    any_of(build_criteria),
    combined_build_criteria,
    interview_rank,
    interview_score
  ) %>%
  # Display to top of the rankings
  filter(combined_build_criteria >= 1 & row_number() <= 15)
```
## Build Award candidates ranking

The first criteria is the one well-described Build Award criterium that can be assessed directly from the data. This report shows the top 15 teams in that criterium. These teams would make good candidates for this award.

`r kbl(build_scores) %>%
  kable_styling()`
