---
title: "Judges Report"
author: "Philip Chase"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(readxl)
library(janitor)
library(httr)
library(kableExtra)
```

```{r event_facts}
matches <- tribble(
  ~event_code, ~date, ~name, ~divisions, ~notebook_file, ~interview_file,
  "RE-VIQC-22-8238", "10-Dec-2022", "WWR December Blended (MS/ES) VEX IQ Tournament", 2,
  "/Users/pbchase/git/vex_matches/output/P & C Robotic Notebooks for 12-10-2022.csv", "",
  "RE-VIQC-21-4702", "6-Nov-2021", "WWR November Pitching In Tournament", 2, "", ""
) %>%
  mutate(notebook_file = if_else(
    !is.na(notebook_file) & notebook_file != "",
    notebook_file,
    here::here("output", paste(event_code, "notebooks.csv", sep = "_"))
  )) %>%
  mutate(interview_file = if_else(
    !is.na(interview_file) & interview_file != "",
    interview_file,
    here::here("output", paste(event_code, "interviews.csv", sep = "_"))
  )) %>%
  mutate(scratch_file = 
    here::here("output", paste(event_code, "scratches.csv", sep = "_")
  )) %>%
  mutate(event_number_for_url = paste0("4", str_remove(event_code, ".*-"))) %>%
  mutate(team_list_url = paste("https://www.robotevents.com/eventEntities",
    event_number_for_url,
    "teamsReport",
    sep = "/"
  )) %>%
  mutate(skills_url = paste("https://www.robotevents.com/eventEntities",
    event_number_for_url,
    "skillsReport",
    sep = "/"
  )) %>%
  mutate(results_url = paste("https://www.robotevents.com/eventEntities",
    event_number_for_url,
    "resultsReport/",
    sep = "/"
  ))

match <- matches %>%
  filter(event_code == "RE-VIQC-22-8238")

# match <- matches %>%
#   filter(event_code == "RE-VIQC-21-4702")

get_xls_from_url <- function(my_url, use_cached_data = TRUE) {
  if (!fs::dir_exists("cache")) {
    fs::dir_create("cache")
  }
  cached_file_name <- here::here("cache", paste0(fs::path_sanitize(my_url), ".xls"))
  if (!fs::file_exists(cached_file_name) | !use_cached_data) {
    message("Fetching data from ", my_url)
    httr::GET(url = my_url, write_disk(cached_file_name, overwrite = T))  
  } else {
    message("Using cached data for ", my_url)
  }
  df <- readxl::read_xls(cached_file_name) %>%
    janitor::clean_names()
  return(df)
}

teams <- get_xls_from_url(match$team_list_url)
```

```{r make_empty_files}
if (!fs::dir_exists("output")) {
  fs::dir_create("output")
}

# Write out an empty Interviews file if it is does not exist
if (!fs::file_exists(match$interview_file)) {
  checked_in_teams %>%
  select(team) %>%
  mutate(interview_score = NA) %>%
    write_csv(match$interview_file, na = "")
}

# Write out an empty notebooks file if it is does not exist
if (!fs::file_exists(match$notebook_file)) {
  checked_in_teams %>%
  select(team) %>%
  mutate(notebook_score = NA) %>%
  write_csv(match$notebook_file, na = "")
}

# Write out an scratch file if it is does not exist
if (!fs::file_exists(match$scratch_file)) {
  teams %>%
  select(team) %>%
  mutate(scratch = 0) %>%
  write_csv(match$scratch_file, na = "")
}
```

```{r arrival_data}
# read the list of scratches from the Event Partner
scratches <- read_csv(match$scratch_file) %>%
  janitor::clean_names() %>%
  filter(scratch == 1) %>%
  mutate(team = toupper(team)) %>%
  pull(team)

checked_in_teams <- teams %>%
  filter(! team %in% scratches)

registered_team_count = nrow(teams)
scratched_team_count = length(scratches)
checked_in_team_count = nrow(checked_in_teams)

```

## Counts

- Registered team count: `r registered_team_count`
- Scratched team count: `r scratched_team_count`

## List of scratched teams
`r scratches`

```{r judging_data, warning=FALSE, echo=FALSE, include=FALSE}
notebooks <- read_csv(match$notebook_file) %>%
  janitor::clean_names() %>%
  mutate(team = toupper(team)) %>%
  arrange(desc(notebook_score)) %>%
  mutate(notebook_rank = if_else(
    is.na(notebook_score) | notebook_score == 0,
    NA_integer_,
    row_number()
  ))

# Judged teams not in registrants
notebook_data_not_in_registrants <- notebooks %>%
  anti_join(checked_in_teams, by="team") %>%
  select(team, notebook_score, notebook_rank)

# registrants not in judged teams
registrants_not_in_notebook_data <- checked_in_teams %>%
  anti_join(notebooks, by="team")

interviews <- read_csv(match$interview_file) %>%
  arrange(desc(interview_score)) %>%
  mutate(interview_rank = if_else(
    is.na(interview_score) | interview_score == 0,
    NA_integer_,
    row_number()
  ))

interviews_completed <- interviews %>%
  filter(!is.na(interview_score)) %>%
  nrow()

interviews_remaining <- nrow(checked_in_teams) - interviews_completed

teams_to_interview <- interviews %>%
  filter(is.na(interview_score)) %>%
  select(team)

judging <- checked_in_teams %>%
  select(team) %>%
  left_join(notebooks, by = "team") %>%
  left_join(interviews, by = "team") %>%
  mutate(judged_score = notebook_score + interview_score) %>%
  arrange(desc(judged_score)) %>%
  mutate(judged_rank = if_else(is.na(judged_score), NA_integer_, row_number()))
```

## Notebook data not in registrants

`r kbl(notebook_data_not_in_registrants) %>%
  kable_styling()`

## Registrants not in notebook data

`r kbl(registrants_not_in_notebook_data) %>%
  kable_styling()`

## Interviews

- Interviewed team count: `r interviews_completed`
- Interviews remaining: `r interviews_remaining`

These teams still need to be recorded in the interview file:

`r kbl(teams_to_interview) %>%
  kable_styling()`

```{r skills, warning=FALSE, include = FALSE, message = TRUE}
# get results of skills competition
skills_results <- get_xls_from_url(match$skills_url)
if (nrow(skills_results) > 0) {
  skills_data <- skills_results %>%
    janitor::clean_names() %>%
    pivot_wider(
      id_cols = c("rank", "team"),
      names_from = c("type"),
      values_from = c("highscore", "attempts")
    ) %>%
    rowwise() %>%
    mutate(highscore_combined = sum(highscore_driver, highscore_programming, na.rm = TRUE)) %>%
    ungroup() %>%
    select(rank, team, highscore_combined, everything()) %>%
    rename(skills_rank = rank)
} else {
  skills_data <- tribble(
    ~skills_rank, ~team, ~highscore_combined, ~highscore_driver, ~highscore_programming,
    1, "asdf", 1, 1, 1
  ) %>% filter(F)
}
```

```{r qualifier_function}
get_qualifier_results_for_division <- function(base_results_url, division) {
  results_url <- paste0(base_results_url, division)
  results <- get_xls_from_url(results_url)
  data <-
    results %>%
    janitor::clean_names() %>%
    rename_with(., ~ gsub("_[0-9]+", "", .x), contains("_team_")) %>%
    pivot_longer(
      cols = c(red_team, blue_team),
      names_to = c("team_color"),
      values_to = c("team_number")
    ) %>%
    pivot_longer(
      cols = c(red_score, blue_score),
      values_to = c("team_score")
    ) %>%
    mutate(team_color = gsub("_team", "", team_color)) %>%
    mutate(name = gsub("_score", "", name)) %>%
    filter(team_color == name) %>%
    mutate(division = division) %>%
    select(division, match, team_color, team_number, team_score)

  return(data)
}
```

```{r qualifiers}
qualifier_results <- tribble(
  ~division, ~match, ~team_color, ~team_number, ~team_score,
  1, "a", "b", "c", 99
) %>% filter(F)

for (division in seq.int(1, match$divisions)) {
  qualifier_results <- bind_rows(qualifier_results, get_qualifier_results_for_division(match$results_url, division = division))
  }

ranked_qualifer_results <- qualifier_results %>%
  rename(team = team_number) %>%
  group_by(team) %>%
  summarize(average_score = mean(team_score, na.rm = T)) %>%
  arrange(desc(average_score)) %>%
  mutate(qualifier_rank = if_else(!is.na(average_score),
    row_number(),
    NA_integer_
  ))
```

```{r excellence_scores}
excellence_skills_count <- max(nrow(skills_data) * 0.2, 5)
excellence_qualifiers_count <- max(nrow(ranked_qualifer_results) * 0.3, 10)
excellence_criteria = c(
  "has_a_notebook",
  "has_an_interview",
  "top_of_skills",
  "top_of_qualifiers"
)
excellence_scores <-
  judging %>%
  # must have a notebook
  mutate(has_a_notebook = !is.na(notebook_score) & notebook_score != 0) %>%
  # must have an interview
  mutate(has_an_interview = !is.na(interview_score) & interview_score != 0) %>%
  # must be in the top 5 or 20% of skills scores
  left_join(
    skills_data %>%
      arrange(skills_rank) %>%
      mutate(top_of_skills = (row_number() <= excellence_skills_count)),
    by = "team"
  ) %>%
  left_join(
    ranked_qualifer_results %>%
      mutate(top_of_qualifiers = (row_number() <= excellence_qualifiers_count)),
    by = "team"
  ) %>%
  rowwise() %>%
  mutate(combined_rank = sum(judged_rank, skills_rank, qualifier_rank)) %>%
  mutate(combined_excellence_criteria = sum(has_a_notebook, has_an_interview, top_of_skills, top_of_qualifiers)) %>%
  arrange(
    desc(combined_excellence_criteria),
    combined_rank,
    judged_rank,
    notebook_rank,
    interview_rank,
    skills_rank,
    qualifier_rank,
    highscore_driver,
    highscore_programming
  ) %>%
  ungroup() %>%
  mutate(excellence_rank = row_number()) %>%
  select(
    team,
    any_of(excellence_criteria),
    combined_excellence_criteria,
    combined_rank,
    judged_rank,
    notebook_rank,
    interview_rank,
    skills_rank,
    qualifier_rank,
    highscore_combined,
    highscore_driver,
    highscore_programming
  ) %>%
  # Display to top of the rankings
  filter(combined_excellence_criteria >= 3 | row_number() <= 10)
```
## Excellence ranking

The first four criteria are the Excellence award criteria that can be assessed directly from the data. `combined_excellence_criteria` is the sum of those four criteria. `combined_rank` is the sum of the judging rank, skills rank and qualifiers rank. 

`r kbl(excellence_scores) %>%
  kable_styling()`


```{r design_scores}
design_criteria = c(
  "has_a_notebook",
  "has_an_interview"
)
design_scores <-
  judging %>%
  # must have a notebook
  mutate(has_a_notebook = !is.na(notebook_score) & notebook_score != 0) %>%
  # must have an interview
  mutate(has_an_interview = !is.na(interview_score) & interview_score != 0) %>%
  rowwise() %>%
  mutate(combined_design_criteria = sum(has_a_notebook, has_an_interview)) %>%
  filter(combined_design_criteria == 2) %>%
  arrange(
    notebook_rank,
    judged_rank,
    interview_rank
  ) %>%
  ungroup() %>%
  select(
    team,
    any_of(design_criteria),
    notebook_rank,
    judged_rank,
    interview_rank
  ) %>%
  # Display to top of the rankings
  filter(row_number() <= 10)
```
## Design ranking

Only the top 10 teams that have both a notebook score and an interview score are shown.  The teams are sorted by Notebook rank and then total judged rank.

`r kbl(design_scores) %>%
  kable_styling()`
