---
title: "Judges Report"
author: "Philip Chase"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(readxl)
library(janitor)
library(httr)
library(kableExtra)
```

```{r event_facts}
matches <- tribble(
  ~event_code, ~date, ~name, ~divisions, ~notebook_file, ~interview_file,
  "RE-VIQC-22-8238", "10-Dec-2022", "WWR December Blended (MS/ES) VEX IQ Tournament", 2,
  "/Users/pbchase/Downloads/P & C Robotic Notebooks for 10-22-2022.xlsx", "",
  "RE-VIQC-21-4702", "6-Nov-2021", "WWR November Pitching In Tournament", 2, "", ""
) %>%
  mutate(notebook_file = if_else(
    !is.na(notebook_file) & notebook_file != "",
    notebook_file,
    here::here("output", paste(event_code, "notebooks.csv", sep = "_"))
  )) %>%
  mutate(interview_file = if_else(
    !is.na(interview_file) & interview_file != "",
    interview_file,
    here::here("output", paste(event_code, "interviews.csv", sep = "_"))
  )) %>%
  mutate(event_number_for_url = paste0("4", str_remove(event_code, ".*-"))) %>%
  mutate(team_list_url = paste("https://www.robotevents.com/eventEntities",
    event_number_for_url,
    "teamsReport",
    sep = "/"
  )) %>%
  mutate(skills_url = paste("https://www.robotevents.com/eventEntities",
    event_number_for_url,
    "skillsReport",
    sep = "/"
  )) %>%
  mutate(results_url = paste("https://www.robotevents.com/eventEntities",
    event_number_for_url,
    "resultsReport/",
    sep = "/"
  ))

match <- matches %>%
  filter(event_code == "RE-VIQC-22-8238")

match <- matches %>%
  filter(event_code == "RE-VIQC-21-4702")

get_xls_from_url <- function(my_url) {
  tmp_file <- tempfile(fileext = ".xls")
  httr::GET(url = my_url, write_disk(tmp_file))
  df <- readxl::read_xls(tmp_file) %>%
    janitor::clean_names()
  fs::file_delete(tmp_file)
  return(df)
}

teams <- get_xls_from_url(match$team_list_url)
```

```{r arrival_data}
# Get the list of scratches from the Event Partner
scratches <- c(
)

checked_in_teams <- teams %>%
  filter(! team %in% scratches)

registered_team_count = nrow(teams)
scratched_team_count = length(scratches)
checked_in_team_count = nrow(checked_in_teams)

```

## Counts

- Registered team count: `r registered_team_count`
- Scratched team count: `r scratched_team_count`

## List of scratched teams
`r scratches`

```{r make_empty_files}
if (!fs::dir_exists("output")) {
  fs::dir_create("output")
}

# Write out an empty Interviews file if it is does not exist
if (!fs::file_exists(match$interview_file)) {
  checked_in_teams %>%
  select(team) %>%
  mutate(interview_score = NA) %>%
    write_csv(match$interview_file, na = "")
}

# Write out an empty notebooks file if it is does not exist
if (!fs::file_exists(match$notebook_file)) {
  checked_in_teams %>%
  select(team) %>%
  mutate(notebook_score = NA) %>%
  write_csv(match$notebook_file, na = "")
}
```

```{r judging_data, warning=FALSE, echo=FALSE, include=FALSE}
notebooks <- read_csv(match$notebook_file) %>%
  janitor::clean_names() %>%
  mutate(team = toupper(team)) %>%
  arrange(desc(notebook_score)) %>%
  mutate(notebook_rank = if_else(is.na(notebook_score), NA_integer_, row_number()))

# Judged teams not in registrants
notebook_data_not_in_registrants <- notebooks %>%
  anti_join(checked_in_teams, by="team") %>%
  select(team)

# registrants not in judged teams
registrants_not_in_notebook_data <- checked_in_teams %>%
  anti_join(notebooks, by="team")

interviews <- read_csv(match$interview_file) %>%
  arrange(desc(interview_score)) %>%
  mutate(interview_rank = if_else(is.na(interview_score), NA_integer_, row_number()))

interviews_completed <- interviews %>%
  filter(!is.na(interview_score)) %>%
  nrow()

interviews_remaining <- nrow(checked_in_teams) - interviews_completed

teams_to_interview <- interviews %>%
  filter(is.na(interview_score)) %>%
  select(team)

judging <- checked_in_teams %>%
  select(team) %>%
  left_join(notebooks, by = "team") %>%
  left_join(interviews, by = "team") %>%
  mutate(judged_score = notebook_score + interview_score) %>%
  arrange(desc(judged_score)) %>%
  mutate(judged_rank = if_else(is.na(judged_score), NA_integer_, row_number()))
```

## Notebook data not in registrants

`r kbl(notebook_data_not_in_registrants) %>%
  kable_styling()`

## Registrants not in notebook data

`r kbl(registrants_not_in_notebook_data) %>%
  kable_styling()`

## Interviews

- Interviewed team count: `r interviews_completed`
- Interviews remaining: `r interviews_remaining`

These teams still need to be recorded in the interview file:

`r kbl(teams_to_interview) %>%
  kable_styling()`

```{r skills, warning=FALSE, include = FALSE, message = FALSE}
# get results of skills competition
skills_results <- get_xls_from_url(match$skills_url)
skills_data <- skills_results %>%
  janitor::clean_names() %>%
  pivot_wider(
    id_cols = c("rank", "team"),
    names_from = c("type"),
    values_from = c("highscore", "attempts")
  ) %>%
  mutate(highscore_combined = highscore_driver + highscore_programming) %>%
  select(rank, team, highscore_combined, everything()) %>%
  rename(skills_rank = rank)
```

```{r qualifier_function}
get_qualifier_results_for_division <- function(base_results_url, division) {
  results_url <- paste0(base_results_url, division)
  tmp_file <- tempfile()
  httr::GET(url = results_url, write_disk(tmp_file))
  results <- readxl::read_xls(tmp_file)
  data <-
    results %>%
    janitor::clean_names() %>%
    rename_with(., ~ gsub("_[0-9]+", "", .x), contains("_team_")) %>%
    pivot_longer(
      cols = c(red_team, blue_team),
      names_to = c("team_color"),
      values_to = c("team_number")
    ) %>%
    pivot_longer(
      cols = c(red_score, blue_score),
      values_to = c("team_score")
    ) %>%
    mutate(team_color = gsub("_team", "", team_color)) %>%
    mutate(name = gsub("_score", "", name)) %>%
    filter(team_color == name) %>%
    mutate(division = division) %>%
    select(division, match, team_color, team_number, team_score)

  return(data)
}
```

```{r qualifiers}
qualifier_results <- tribble(
  ~division, ~match, ~team_color, ~team_number, ~team_score,
  1, "a", "b", "c", 99
) %>% filter(F)

for (division in seq.int(1, match$divisions)) {
  qualifier_results <- bind_rows(qualifier_results, get_qualifier_results_for_division(match$results_url, division = division))
  }

ranked_qualifer_results <- qualifier_results %>%
  rename(team = team_number) %>%
  group_by(team) %>%
  summarize(average_score = mean(team_score)) %>%
  arrange(desc(average_score)) %>%
  mutate(qualifier_rank = row_number())
```

```{r combined_results}
combined_scores <-
  judging %>%
  left_join(skills_data, by = "team") %>%
  left_join(ranked_qualifer_results, by = "team") %>%
  rowwise() %>%
  mutate(combined_rank = if_else(
    is.na(coalesce(skills_rank, qualifier_rank, judged_rank)),
    NA_real_,
    sum(skills_rank, qualifier_rank, judged_rank, na.rm = T)
  )) %>%
  select(team, combined_rank, contains("rank"), everything()) %>%
  arrange(combined_rank)
```

## Combined ranking

The combined ranking for Judging, Skills and Qualifiers is

`r kbl(combined_scores) %>%
  kable_styling()`
